### 2020-10-28 doc/manuscript/Dow_manuscript.Rmd
add dendroband numbers

Within the plot, metal dendrometer bands were installed on *>#* trees and measured with a digital caliper approximately every 1-2 weeks within the growing season for *9* years (*list ranges, for each site if different*). *(don't bother to mention biannual bands, unless you end up using the data--which you could, for annual growth, if you'd like to increase the sample size. You can put exact numbers of bands per year in an SI file.*)  The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census (Table `r sample_size_by_year`). Across years, the number of bands sampled averaged *~150* at SCBI, # at Harvard Forest*, and # at SERC*. Four main species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species.    *(summary of how bands were distributed across species, focusing on ring/ diffuse porous distinction. details in an SI table)*

(5 years @ Harvard Forest, 10 @ SCBI)

>>>>

Metal dendrometer bands installed on *700-755* trees at Harvard Forest and *99-145* trees at SCBI were measured with a digital caliper approximately every 1-2 weeks within the growing season from 1998-2003, and 2011-2020 respectively (*list ranges, for each site if different*). *(don't bother to mention biannual bands, unless you end up using the data--which you could, for annual growth, if you'd like to increase the sample size. You can put exact numbers of bands per year in an SI file.*)  The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census (Table `r sample_size_by_year`) (tags_per_year_preclean in data folder). Across years, the number of bands sampled averaged *~135* at SCBI, *~717* at Harvard Forest*, and # at SERC*. At SCBI, 4 species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species. At Harvard Forest, 11 species were sampled including 8 diffuse-porous and 3 ring-porous (SI table)(bands_bySP csv's in data folder).      *(summary of how bands were distributed across species, focusing on ring/ diffuse porous distinction. details in an SI table)*
